\documentclass[7pt]{article}

\usepackage{variables}

\usepackage{fontspec}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage[none]{hyphenat}
\usepackage{longtable}

\def\middot{\textperiodcentered~}

\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name: \name},
  pdfkeywords = {David, Richards, software, developer, Brighton},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
 a4paper,
 total={170mm,257mm},
 left=5mm,
 right=15mm,
 top=10mm,
 bottom=10mm,
}

\setmainfont{Lato}
\pagestyle{empty}

\setlength\parindent{0em}

\renewcommand{\labelitemii}{$\bullet$}

\nopagebreak[4]

\begin{document}

\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{1.0\textwidth}
  \centering
  \address
  \break
  \href{mailto:\email}{\email}
  \middot \href{tel:\phone}{\phone}
  \break
  \href{https://dcrichards.com/}{dcrichards.com}
  \middot \href{https://github.com/DCRichards}{github.com/DCRichards} 
\end{minipage}

\vspace{0.25in}

\begin{tabular}{@{} p{0.15\textwidth} p{0.85\textwidth}}
  \textbf{EDUCATION} & \begin{minipage} [t] {0.85\textwidth} 2011 - 2015 \href{https://sussex.ac.uk/}{\textbf{University of Sussex}}, Brighton \\
  \textbf{First Class}: BSc (Hons) Computer Science (with an Industrial Placement Year) \\
  \newline
    Final Year Project: Two-factor Authentication in Wearable Technologies, developing a two-factor authentication application for the Pebble Smartwatch and Google Glass using Time-Based One-Time Passwords (TOTP). \\
    \newline
    Notable Modules:
    \begin{itemize}
      \setlength\itemsep{-4pt}
      \item Web Applications \& Services (J2EE, JSF, GlassFish, Java DB, AWS)
      \item Databases (SQL)
      \item Machine Learning, Natural Language Engineering (Python)
      \item Comparative Programming (Haskell, Prolog)
      \item Compilers \& Computer Architecture (MIPS, x86)
    \end{itemize}
    Additional Experience:
    \begin{itemize}
      \item Student Life speaker for Informatics Applications Visit Days, giving talks on course content and experience to prospective students and parents.
    \end{itemize}
  \end{minipage} \\
  & \\
  & 2009-2011 South Downs College, Waterlooville \\
  & A Level: Computing (A), Mathematics (B), Chemistry (B) \\
  & \\
  & 2004-2009 Park Community School, Havant \\
  & GCSE: 11 subjects A* to B grade including Maths (A*) and English (A) \\
\end{tabular}

\vspace{0.25in}

\begin{longtable}{@{} p{0.15\textwidth} p{0.85\textwidth}}
  \textbf{PROFESSIONAL EXPERIENCE} & \begin{minipage} [t] {0.85\textwidth}
    February 2016 - Present \href{https://ocasta.com}{\textbf{Ocasta}, Brighton} \middot Software Developer \\
    \newline
    Ocasta specialise in apps, web and everything in between. Ocasta are also the creators of the Oplift customer engagement platform.
    \begin{itemize}
      \setlength\itemsep{-1pt}
      \item Android development on a number widely-used of applications, including Virgin Media WiFi, providing WiFi Hotspot access to over 500,000 customers. Making use of modern Android tooling, including Kotlin/Java with RxJava, Retrofit 2, Robolectric, Espresso, Room and Android Architecture/Lifecycle Components.
      \item Technical lead on the Home WiFi project, extending Virgin Media WiFi to provide customers with direct control of their router. This included building an abstracted REST API on top of the SNMP over REST API provided.
      \item Server development in Node.js (Hapi.js/Koa, Mocha/Chai, JSHint/Eslint, MongoDB) and microservice development in Go.
      \item Writing and maintaining technical API documentation in API Blueprint.
      \item Wordpress development (PHP, Hack(lang)/HHVM) to provide REST API access to CMS content.
      \item Collaborating closely with the design team to build UI to design specifications and provide feedback. Making use of design collaboration tools such as Sketch and Zeplin.
      \item Managing multiple agile processes including story estimation and prioritisation both within and across multiple projects.
    \end{itemize}
  \end{minipage} \\
  & \\
  & \begin{minipage} [t] {0.85\textwidth}
    January 2018 - Present \href{https://www.hiddenfield.com}{\textbf{HiddenField}} \middot Contract Developer (Remote)\\
    \newline
    HiddenField deliver cyber security products through agile solutions.
    \begin{itemize}
      \item Current project includes hardware wallet integration for a leading crypto organisation, building an end-to-end testing framework between device and client to ensure integrity, security and testability across all stages of the development process.
    \end{itemize}
  \end{minipage} \\
  & \\
  & \begin{minipage} [t] {0.85\textwidth}
    July 2015 - December 2015 \textbf{Mobbu}, Brighton \middot Developer \\
    \newline
    Rejoined the team at Mobbu to work on their new flagship product PassWear: A mobile and smartwatch based two-factor authentication solution.
    \begin{itemize}
      \setlength\itemsep{-1pt}
      \item Developed a large proportion of the PassWear Android SDK, including writing of the high-level API, integration with wearables and high level and API documentation.
      \item Development of wearable applications on Pebble (C), Android Wear (Java) and Apple Watch (Objective-C).
      \item Development of mobile application on both Android (Java, Gradle) and iOS (Objective-C).
      \item Continued work within the agile development team, this time using Kanban maintained by Jira and code reviews using Crucible.
      \item Managed internal dependencies using Maven and Nexus repository manager.
    \end{itemize}
  \end{minipage} \\
  & \\
  & \begin{minipage} [t] {0.85\textwidth}
    August 2013 - August 2014 \textbf{Mobbu}, Brighton \middot Intern Developer \\
    \newline
    Undertaken for my Industrial Placement Year. I joined the team during the transition from single to cross-platform mobile applications and during other web and mobile based projects.
    \begin{itemize}
      \setlength\itemsep{-1pt}
      \item Worked as part of a small Agile software development team, took part in daily stand-up meetings, retrospectives and sprint reviews and used story pointing for task estimation.
      \item Web application development in JavaScript (including using Ractive.js templating/UI library)
      \item Mobile application development using Apache Cordova on BlackBerry and Android platforms.
      \item Unit testing using QUnit/Jasmine and integration testing using CasperJS and PhantomJS.
      \item Developed RESTful Web Services in Java (JAX-RS) and Node.js including interaction with SQL Server database.
      \item Improved automation, build and deployment tools using Grunt and Ant and integrated with the Jenkins Continuous Integration server.
      \item Providing training and guidance for interns on the development processes and technology stack to ensure a smooth changeover at the end of my placement.
      \item Used Subversion and Git version control.
      \item Used Windows (IIS, Windows Server), OSX and Unix (Ubuntu) environments, including Unix command line.
    \end{itemize}
  \end{minipage}
\end{longtable}

\vspace{0.25in}

\begin{tabular}{@{} p{0.15\textwidth} p{0.85\textwidth}}
  \textbf{PERSONAL PROJECTS} & \textbf{Should I Eat There?} Written in Vue.js 2.x, Should I Eat There? provides a simpler way to find the Food Hygiene rating of your favourite establishments. It can be found at \href{http://shouldieatthere.co.uk}{shouldieatthere.co.uk}. \\
  & \\
  & I have also made a number of open-source contributions to projects such as Glide, Bintray, Robolectric (Android) and Drone CI.
\end{tabular}

\vspace{0.25in}

\begin{tabular}{@{} p{0.15\textwidth} p{0.85\textwidth}}
  \textbf{VOLUNTEER EXPERIENCE} & \textbf{Codebar Brighton (Coach)}: Codebar provides programming tuition to under-represented groups. As well as providing coaching at sessions, I recently co-presented an interactive Git workshop, teaching Git to Codebar students. \\
\end{tabular}

\vspace{0.25in}

\begin{tabular}{@{} p{0.15\textwidth} p{0.85\textwidth}}
  \textbf{OTHER} & Full, Clean UK Driving License
\end{tabular}

\vspace{0.25in}

\begin{tabular}{@{} p{0.15\textwidth} p{0.85\textwidth}}
  \textbf{REFERENCES} & References are available upon request.
\end{tabular}

\bigskip

\end{document}
