\documentclass{article}

\usepackage{array}
\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage{fontspec}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{titlesec}
\usepackage{variables}
\usepackage{xcolor}

\geometry{a4paper, top=1cm, bottom=1cm, left=0.9cm, right=1.5cm}

\setsansfont[Ligatures=TeX,Scale=0.9]{Work Sans}
\setmainfont[Ligatures=TeX,Scale=0.9]{Lora}

\titleformat{\section}{\sffamily\Large}{\thesection}{0em}{}[{\titlerule[0.5pt]}]
\titlespacing\section{0em}{0em}{0pt plus 1em minus 1em}

\pagenumbering{gobble}
\hypersetup{hidelinks}

\newenvironment{exptable}{
  \begin{longtable}{lp{0.8\textwidth}}
  }{
  \end{longtable}
}
\setlist[itemize]{itemsep=0pt, topsep=0.25em, leftmargin=2em}

\begin{document}
  \begin{center}
    {\Huge \sffamily\selectfont \MakeUppercase{\textmd{\name}}}
  \end{center}

  \begin{minipage}[t]{0.6\textwidth}
    \raggedright
    \href{mailto:\email}{\email} \\
    \href{tel:\phone}{\phone} \\
    \address
  \end{minipage}
  \begin{minipage}[t]{0.35\textwidth}
    \raggedleft
    \smallskip
    \href{https://dcrichards.com}{https://dcrichards.com} \\
    \href{https://github.com/DCRichards}{github.com/DCRichards} \\
  \end{minipage}

  \vspace{1em}

  \section*{SUMMARY}
  \vspace{1em}
  Motivated, detail-oriented developer with expertise in server-side, front-end and Android mobile development. I am able to dive deeply into a platform whilst providing valuable visibility and skills across the stack.
  \vspace{1em}

  \section*{PROFESSIONAL EXPERIENCE}
    \begin{exptable}
      \textcolor{darkgray}{May 2019--Present}  & \textbf{Head of Development} HiddenField, Remote \\
      \multicolumn{2}{p{\textwidth}}{
        \begin{itemize}
          \item Technical Lead for Coincover project, a web platform for providing theft protection and recovery for Cryptocurrency wallets.
          \item Front-end development of the Vue.js web application and using this to shape the core Vue.js template across projects.
          \item Building and integrating Go service with numerous external REST services, evolving architecture and implementation to overcome the associated challenges.
          \item Responsible for planning and architecting solutions, documenting and producing estimations and epics and stories for them.
        \end{itemize}

        \vspace{1em}

        \begin{itemize}[leftmargin=1em]
          \item[] Technologies: Vue.js, Node.js, Go, HTML, JS (ES6), CSS, MongoDB, Docker, JIRA, LucidChart
        \end{itemize}
      } \\

      \textcolor{darkgray}{Sep 2018--Apr 2019} & Career Break: Travelling \\
      \multicolumn{2}{p{\textwidth}}{} \\

      \textcolor{darkgray}{Jan 2018--Sep 2018} & \textbf{Contract Developer} HiddenField, Remote \\
      \multicolumn{2}{p{\textwidth}}{
        \begin{itemize}
          \item Added Cardano ADA coin support to the Ledger Nano S Hardware Wallet, building an end-to-end test framework to test the integration of the native C code with the Node.js SDK. Once complete, I integrated the ADA SDK into the Ledger open-source repository.
          \item Developed the initial proof of concept for what would later become Coincover using Go and Vue.js.
        \end{itemize}

        \vspace{1em}

        \begin{itemize}[leftmargin=1em]
          \item[] Technologies: Node.js (Mocha/Chai, Typescript/Flow, Prettier), C, Vagrant, Go, Vue.js.
        \end{itemize}
      } \\
      \textcolor{darkgray}{Feb 2016--Aug 2018} & \textbf{Software Developer} Ocasta, Brighton \\
      \multicolumn{2}{p{\textwidth}}{
        \begin{itemize}
          \item Android developer on a number of widely-used applications such as EasyCar Club and Virgin Media WiFi, providing WiFi Hotspot access to over 500,000 customers.
          \item Migrating Android applications to Kotlin and Architecture Components and evolving the company Android template to the changing Android landscape and current Material Design standards.
          \item Technical lead on the Home WiFi project, extending Virgin Media WiFi app to provide customers with direct control of their router. This included building an abstracted REST API on top of the SNMP over REST API provided.
          \item Developing RESTful and GraphQL services and microservices in Go and Node.js, as well as managing their development and production environments using Docker and Drone CI. This included integrating these with existing micro and monolithic services.
        \end{itemize}

        \vspace{1em}

        \begin{itemize}[leftmargin=1em]
          \item[] Technologies: Android (Kotlin and Java, RxJava/Android, Retrofit2, Robolectric, Espresso, Room, Architecture/Lifecycle Components), Go, Node.js (Hapi/Koa, Mocha/Chai, Eslint), Docker (Docker Hub, Rancher), MongoDB, GraphQL, HTML, CSS.
        \end{itemize}
      } \\
      \textcolor{darkgray}{Jul 2015--Dec 2015} & \textbf{Developer} Mobbu, Brighton \\
      \multicolumn{2}{p{\textwidth}}{
        \begin{itemize}
          \item Developed a large proportion of the PassWear Android SDK. This included the design and implementation of the API as an Android Library as well as technical documentation.
          \item Development of wearable applications on Pebble, Android Wear and Apple Watch.
          \item Developed mobile application on both Android and iOS, including modularising part of the Android application for the SDK using modules. Managed internal dependencies using Maven and Nexus repository manager.
          \item Continued work within the agile development team, this time using Kanban maintained by Jira and code reviews using Crucible.
        \end{itemize}

        \vspace{1em}

        \begin{itemize}[leftmargin=1em]
          \item[] Technologies: Android (Java, Modules using Gradle/Maven), iOS (Objective-C), C.
        \end{itemize}
      } \\

      \clearpage

      \textcolor{darkgray}{Aug 2013--Aug 2014} & \textbf{Intern Developer (Placement Year)} Mobbu, Brighton \\
      \multicolumn{2}{p{\textwidth}}{
        \begin{itemize}
          \item Worked as part of a small Agile software development team, took part in daily stand-up meetings, retrospectives and sprint reviews and used story pointing for task estimation.
          \item Web application development for a messaging and mapping client with unit and integration testing within a headless browser (PhantomJS).
          \item Mobile application development using Apache Cordova on BlackBerry and Android platforms.
          \item Developed RESTful Web Services in Java and Node.js, with data stored in SQL Server.
          \item Improved automation, build and deployment tools using both Grunt and Ant and integrated with Jenkins CI.
          \item Providing training and guidance for interns on the development processes and technology stack to ensure a smooth changeover at the end of my placement.
        \end{itemize}

        \vspace{1em}

        \begin{itemize}[leftmargin=1em]
          \item[] Technologies: JS (Ractive.js templating, QUnit/Jasmine, CasperJS, PhantomJS), Apache Cordova (Blackberry/Android), Java (JAX-RS), SQL Server, Jenkins CI, Grunt, Ant.
        \end{itemize}
      } \\
    \end{exptable}

  \vspace{-1em}

  \section*{EDUCATION}
    \begin{exptable}
      \textcolor{darkgray}{2011--2015} & {\bf University Of Sussex}, Brighton \\
                 & {\bf First Class}: BSc (Hons) Computer Science (with an Industrial Placement Year) \\
                 & \\
      \multicolumn{2}{p{\textwidth}}{
      Final Year Project: Two-factor Authentication in Wearable Technologies, developing a two-factor authentication application for the Pebble Smartwatch and Google Glass using Time-Based One-Time Passwords (TOTP).
      } \\
                 & \\
      \textcolor{darkgray}{2009--2011} & South Downs College, Havant \\
                 & A Level: Computing (A), Mathematics (B), Chemistry (B) \\
                 & \\
      \textcolor{darkgray}{2004--2009} & Park Community School, Havant \\
                 & GCSE: 11 subjects A* to B grade including Maths (A*) and English (A)
    \end{exptable}

 \section*{PERSONAL PROJECTS}
 \vspace{1em}
  \begin{itemize}
    \item \href{http://shouldieatthere.co.uk}{\textbf{shouldieatthere.co.uk}}: A simple SPA written in Vue.js, allowing users to view the Food Hygiene rating of any UK establishment. Currently deployed on AWS.
    \item \textbf{Curriculum Vitae}: This document is typeset in LaTeX. My current workflow uses Docker for continuous compilation and PDF generation.
  \end{itemize}
 \vspace{1em}

 \section*{VOLUNTEER EXPERIENCE}
  \vspace{1em}
  \begin{itemize}
    \item \href{https://codebar.io/brighton}{\textbf{Codebar Brighton}}: Codebar provides programming tuition to under-represented groups. As well as providing coaching at sessions, I developed and presented an interactive Git workshop, teaching Git version control to Codebar attendees. I later presented the talk at Async.js (Brighton JS Meetup).
    \item \href{https://www.coderdojobrighton.co.uk}{\textbf{CoderDojo}}: Assisted in teaching children simple programming skills in Scratch, Python and Java.
  \end{itemize}
  \vspace{1em}

 \section*{PERSONAL INTERESTS}
  \vspace{1em}
  \begin{itemize}
    \item I love travel and culture. Last year I planned and completed a seven month trip around Southeast Asia and Australasia.
    \item I also enjoy cooking, road cycling, photography and playing and recording music, although not all at the same time.
  \end{itemize}
  \vspace{1em}

 \section*{OTHER}
  \vspace{1em}
  \begin{itemize}
    \item Full, clean UK Driving Licence.
  \end{itemize}
  \vspace{1em}

  \section*{REFERENCES}
    \vspace{1em}
    References are available upon request.

\end{document}
